%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Steven Chen} \\ \vspace{1pt}
    \small 512-785-4271 $|$ \href{mailto:contact@stevenchen.one}{\underline{contact@stevenchen.one}} $|$ 
    \href{https://stevenchen.one/}{\underline{stevenchen.one}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Texas at Austin}{Austin, TX}
      {Bachelor of Science in Electrical and Computer Engineering; GPA: 3.9}{Aug 2022 -- May 2026}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {DevOps/Cloud Engineering Intern}{May 2025 -- Aug 2025}
      {IBM}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Migrated CI pipeline to deploy a new Rust-based HSM binary, replacing legacy C++ integration.}
        \resumeItem{Implemented role-checking logic to verify IAM permissions for hardware HSM access during pipeline executions.}
        \resumeItem{Tested and documented integration of a vendor tool enabling smart card-based authentication for secure HSM access.}
        \resumeItem{Added grouping functionality to run batch read-only operations across HSMs, simplifying compliance audits.}
        \resumeItem{Maintained internal Slack bot by fixing interactive UI flows, investigating TLS handshake issues, and designing key rotation.}
      \resumeItemListEnd
      
    \resumeSubheading
      {DevOps/IT Intern}{Jun 2024 -- May 2025}
      {ERCOT}{Taylor, TX}
      \resumeItemListStart
        \resumeItem{Designed a modular Python automation framework to integrate dependency-based Jira Plans with any API-driven tool.}
        \resumeItem{Created a proof of concept leveraging Jira and Ansible Tower APIs to automate issue tracking, dependency resolution, and playbook execution.}
        \resumeItem{Integrated Microsoft Teams for real-time alerts, manual task notifications, and bi-directional Jira ticket updates from chat.}
        \resumeItem{Developed a custom CytoscapeJS visualization plugin for near real-time status tracking of Jira Plans within Splunk dashboards.}
    \resumeItemListEnd

    \resumeSubheading
      {Backend Developer}{Jan 2024 -- Dec 2024}
      {Texas Luminescence}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Collaborated with the backend team to develop a REST API using Flask and MySQL for a journaling web application.}
        \resumeItem{Wrote Dockerfiles and configured Docker Compose to containerize the app and manage service dependencies.}
        \resumeItem{Deployed the full application stack on Azure using Docker Compose, configured DNS via Route 53, and secured traffic with Let's Encrypt TLS certificates.}
        \resumeItem{Authored comprehensive documentation to help onboard new developers in the organization.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Homelab}}{Aug 2018 -- Present}
          \resumeItemListStart
            \resumeItem{Configured and maintained a homelab environment running Git, Jellyfin, Bitwarden, Nextcloud, game servers, and a personal website.}
            \resumeItem{Used Proxmox as the hypervisor to manage virtual machines and TrueNAS for centralized storage via iSCSI, NFS, and SMB.}
            \resumeItem{Configured pfSense to segment the network using VLANs and firewall rules, isolating services and enforcing access control.}
            \resumeItem{Automated VM provisioning and system configuration using Ansible to reduce manual setup.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Personal Website Upgrade}}{Aug 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Provisioned Talos Linux nodes on Proxmox using a Terraform provider and applied machine configurations to bootstrap a Kubernetes cluster.}
            \resumeItem{Deployed a production-ready cluster with Cilium CNI, Longhorn for distributed storage, and Gateway API with cert-manager for secure service exposure.}
            \resumeItem{Set up Woodpecker CI to build the website from Markdown content and containerize the output.}
            \resumeItem{Used Argo CD with GitOps workflows to continuously deploy website updates from Gitea repositories.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{CCNA, C/C++, Python, Git, Splunk, Virtualization, Cloud-Init, Linux, Bash, Docker, Terraform, Ansible, Talos, Kubernetes, Cilium, Longhorn, NGINX, Woodpecker CI, Argo CD}}
 \end{itemize}


%-------------------------------------------
\end{document}